### 2014-04-16 brains-protocol.tex
Add guiding remark for 3.3

The main question in this problem concerns the way we consider later occurrences of a quotation which, when it first appeared, was identified to be an alteration from an original quotation.
Let us give an example: say the quotation ``These accusations are false and absurd'' ($q_a$) appears in a blog on January 18, and the slightly different quotation ``These accusations are false and incoherent'' ($q_b$) appears in another blog on the 19th, the 20th, and the 21st of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the author of $q_b$ on the 19th based himself on $q_a$.
But what about the following occurrences of $q_b$?
Should we consider them to be substitutions based on $q_a$ (i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) or reproductions of the first occurrence of $q_b$?

>>>>

The main question in this problem concerns the way we consider later occurrences of a quotation which, when it first appeared, was identified to be an alteration from an original quotation.
\rk{it's a balance between repetition, substitution, or injection from outside/other process from inside}
Let us give an example: say the quotation ``These accusations are false and absurd'' ($q_a$) appears in a blog on January 18, and the slightly different quotation ``These accusations are false and incoherent'' ($q_b$) appears in another blog on the 19th, the 20th, and the 21st of January.
If $q_a$ was sufficiently prominent when $q_b$ first appeared, we can safely assume that the author of $q_b$ on the 19th based himself on $q_a$.
But what about the following occurrences of $q_b$?
Should we consider them to be substitutions based on $q_a$ (i.e. re-creations of $q_b$ by a new instance of the substitution process that brought from $q_a$ to $q_b$ in the first place) or reproductions of the first occurrence of $q_b$?
